The Astropy Project

### 2017-11-11 main.tex
footnote anaconda

\python has become especially popular in the quantitative sciences, especially
where researchers must simultaneously produce research, perform data analysis,
and develop software.
A large part of this success owes itself to a vibrant community of developers
and a continuously-growing ecosystem of tools and web services that enable
easier collaboration on software development, easier writing and sharing
documentation, and continuous testing and validation of software.
More recently, package managers such as Anaconda\url{https://anaconda.org/} have
streamlined the installation process for most packages, therefore significantly
reducing the barrier to entry for using many such libraries.

>>>>

\python has become especially popular in the quantitative sciences, especially
where researchers must simultaneously produce research, perform data analysis,
and develop software.
A large part of this success owes itself to a vibrant community of developers
and a continuously-growing ecosystem of tools and web services that enable
easier collaboration on software development, easier writing and sharing
documentation, and continuous testing and validation of software.
More recently, package managers such as
Anaconda\footnote{\url{https://anaconda.org/}} have streamlined the installation
process for most packages, therefore significantly reducing the barrier to entry
for using many such libraries.
